The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
rm header fig caps+interprets
edit network metrics

### Network metrics
We used a series of metrics to characterize the multilayer networks focusing on
the relevance of individual layers, similarity of layers and the role of
individuals. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
unique neighbours, we measured the connective redundancy, the proportion of
neighbours repeated in multiple layers, and the layer relevance, the proportion
of neighbours present compared to the neighbourhood for each individual
[@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
strength for each individual for each layer specific season and landcover
context <!-- citation?-->. Finally, we calculated the similarity of layers
between seasons, across landcover classes (e.g.: winter open compared to summer
open) using the Pearson correlation coefficient [@Br_dka_2018].

@@

* Relevance: layer centric metric, corresponding to the number of neighbours on a
layer divided by the total neighbourhood for each actor. High relevance means
that the layer is highly relevant to the individuals connections. A low
relevance means this layer does not contribute many neighbours to an individuals
overall neighbourhood.

>>>>

### Network metrics
We used a series of metrics to characterize the multilayer networks, focusing on
the the role of individuals and the similarity and relevance of individual layers. Degree
centrality, the number of direct connections an individual has to other individuals in the
network, is the basis of many calculations. We calculated multidegree, the sum of degree
centrality across layers, and neighbourhood, the sum of unique neighbours to each
individual[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
unique neighbours, we measured the connective redundancy, the proportion of
neighbours repeated in multiple layers, and the layer relevance, the proportion
of neighbours present compared to the neighbourhood for each individual
[@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
strength, degree weighted by the values of the tie, for each individual for each 
layer-specific season and landcover context <!-- citation?-->. Finally, we calculated the 
similarity of layers between seasons, across landcover classes (e.g.: winter open compared 
to summer open) using the Pearson correlation coefficient [@Br_dka_2018].

@@

* Relevance: layer centric metric, corresponding to the number of neighbours on a
layer divided by the total neighbourhood for each actor. High relevance = the layer is highly relevant to the individuals connections. A low
relevance means this layer does not contribute many neighbours to an individuals
overall neighbourhood.
